investigating_auprc

### 2019-05-19 Scripts/evaluating_feature_reduction.Rmd
editted results scripts

>>>>

enet_ratios_gm12878_summ$Resolution <- factor(enet_ratios_gm12878_summ$Resolution, levels=c("10 kb", "25 kb", "50 kb", "100 kb"))

ggplot(enet_ratios_gm12878_summ, aes(fill=Annotation, y=AveRatio, x=Resolution)) + 
    geom_bar(stat="identity", position = position_dodge()) +
    geom_errorbar(aes(ymin=AveRatio-AveRatioSD, ymax=AveRatio+AveRatioSD), width=.5,
                 position=position_dodge(.9), alpha=0.75) +
    xlab("Resolution") +
    ylab("Proportion of Features in Final Model") +
    scale_fill_discrete(name="Annotation\nGroup")+
    theme_bw() +
    theme(axis.text.x = element_text(size=15,
                                     angle = 45,
                                     hjust = 1),
          axis.text.y = element_text(size = 10),
          axis.title.x = element_text(size = 20),
          axis.title.y = element_text(size = 20),
          legend.text=element_text(size=15),
          legend.title=element_text(size=20))

### 2019-05-19 Scripts/investigating_auprc.Rmd
editted results scripts

```{r}
auprcdata_gm12878 <- numeric()
pdata_gm12878 <- numeric()
rdata_gm12878 <- numeric()
f1data_gm12878 <- numeric()

@@

@@

pr_results_gm12878 <- cbind.data.frame(AUPRC=auprcdata_gm12878,
                                       Precision=pdata_gm12878,
                                       Recall=rdata_gm12878,
                                       F1=f1data_gm12878,
                                       Predictor=rep(c("Distance", "OC", "OP"), 336),
                                       Resampling=rep(c(rep("None",3),
                                                    rep("ROS", 3),
                                                    rep("RUS", 3),
                                                    rep("SMOTE", 3)),84),
                                       Chromosome=rep(c(rep("CHR1",12),
                                                     rep("CHR2",12),
                                                     rep("CHR3",12),
                                                     rep("CHR4",12),
                                                     rep("CHR5",12),
                                                     rep("CHR6",12),
                                                     rep("CHR7",12),
                                                     rep("CHR8",12),
                                                     rep("CHR10",12),
                                                     rep("CHR11",12),
                                                     rep("CHR12",12),
                                                     rep("CHR13",12),
                                                     rep("CHR14",12),
                                                     rep("CHR15",12),
                                                     rep("CHR16",12),
                                                     rep("CHR17",12),
                                                     rep("CHR18",12),
                                                     rep("CHR19",12),
                                                     rep("CHR20",12),
                                                     rep("CHR21",12),
                                                     rep("CHR22",12)),4),
                                       Resolution=c(rep("10 kb", 21*12),
                                                     rep("25 kb", 21*12),
                                                     rep("50 kb", 21*12),
                                                     rep("100 kb", 21*12)))

@@

pr_results_gm12878_summ <- pr_results_gm12878 %>%
  dplyr::group_by(Resolution, Resampling, Predictor) %>%
  dplyr::summarise(auprc = mean(AUPRC, na.rm = TRUE),
            auprcSD = sd(AUPRC, na.rm = TRUE),
            precision = mean(Precision, na.rm = TRUE),
            precisionSD = sd(Precision, na.rm = TRUE),
            recall = mean(Recall, na.rm = TRUE),
            recallSD = sd(Recall, na.rm = TRUE),
            f1 = mean(F1, na.rm = TRUE),
            f1SD = sd(F1, na.rm = TRUE))

@@

>>>>

```{r}
auprcdata_gm12878 <- numeric()
pdata_gm12878 <- numeric()
rdata_gm12878 <- numeric()
f1data_gm12878 <- numeric()
tpdata_gm12878 <- numeric()
fpdata_gm12878 <- numeric()
tndata_gm12878 <- numeric()
fndata_gm12878 <- numeric()

@@

			  tndata_gm12878 <- rbind(tndata_gm12878, 
			                          perfdata[1,2])

			  fndata_gm12878 <- rbind(fndata_gm12878, 
			                          perfdata[2,2])

			  fpdata_gm12878 <- rbind(fpdata_gm12878, 
			                          perfdata[3,2])

			  tpdata_gm12878 <- rbind(tpdata_gm12878, 
			                          perfdata[4,2])

@@

pr_results_gm12878 <- cbind.data.frame(TN=tndata_gm12878,
                                       FN=fndata_gm12878,
                                       FP=fpdata_gm12878,
                                       TP=tpdata_gm12878,
                                       AUPRC=auprcdata_gm12878,
                                       Precision=pdata_gm12878,
                                       Recall=rdata_gm12878,
                                       F1=f1data_gm12878,
                                       Predictor=rep(c("Distance", "OC", "OP"), 336),
                                       Resampling=rep(c(rep("None",3),
                                                    rep("ROS", 3),
                                                    rep("RUS", 3),
                                                    rep("SMOTE", 3)),84),
                                       Chromosome=rep(c(rep("CHR1",12),
                                                     rep("CHR2",12),
                                                     rep("CHR3",12),
                                                     rep("CHR4",12),
                                                     rep("CHR5",12),
                                                     rep("CHR6",12),
                                                     rep("CHR7",12),
                                                     rep("CHR8",12),
                                                     rep("CHR10",12),
                                                     rep("CHR11",12),
                                                     rep("CHR12",12),
                                                     rep("CHR13",12),
                                                     rep("CHR14",12),
                                                     rep("CHR15",12),
                                                     rep("CHR16",12),
                                                     rep("CHR17",12),
                                                     rep("CHR18",12),
                                                     rep("CHR19",12),
                                                     rep("CHR20",12),
                                                     rep("CHR21",12),
                                                     rep("CHR22",12)),4),
                                       Resolution=c(rep("10 kb", 21*12),
                                                     rep("25 kb", 21*12),
                                                     rep("50 kb", 21*12),
                                                     rep("100 kb", 21*12)))

@@

pr_results_gm12878_summ <- pr_results_gm12878 %>%
  dplyr::group_by(Resolution, Resampling, Predictor) %>%
  dplyr::summarise(auprc = mean(AUPRC, na.rm = TRUE),
            auprcSD = sd(AUPRC, na.rm = TRUE),
            precision = mean(Precision, na.rm = TRUE),
            precisionSD = sd(Precision, na.rm = TRUE),
            recall = mean(Recall, na.rm = TRUE),
            recallSD = sd(Recall, na.rm = TRUE),
            f1 = mean(F1, na.rm = TRUE),
            f1SD = sd(F1, na.rm = TRUE),
            tn = mean(TN, na.rm = TRUE),
            tnSD = sd(TN, na.rm = TRUE),
            fn = mean(FN, na.rm = TRUE),
            fnSD = sd(FN, na.rm = TRUE),
            fp = mean(FP, na.rm = TRUE),
            fpSD = sd(FP, na.rm = TRUE),
            tp = mean(TP, na.rm = TRUE),
            tpSD = sd(TP, na.rm = TRUE))

@@

#TP
tpplot <- ggplot(pr_results_gm12878_summ, aes(x=Resolution, y=tp, color=Resampling, group=Resampling)) +
     geom_line(size=2, position=position_dodge(0.5))+
     geom_point(size=5, position=position_dodge(0.5))+
     geom_errorbar(aes(ymin=tp-tpSD, ymax=tp+tpSD), width=1,
                 position=position_dodge(0.5)) +
     facet_grid(~ Predictor)+
     theme_minimal() +
     theme_bw()+
     xlab("") + ylab("True Positives") + #ylim(-.05,.5) +
     scale_color_discrete(name="Resampling Technique")+
     guides(shape=FALSE, linetype=FALSE)+
     theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

#FP
fpplot <- ggplot(pr_results_gm12878_summ, aes(x=Resolution, y=fp, color=Resampling, group=Resampling)) +
     geom_line(size=2, position=position_dodge(0.5))+
     geom_point(size=5, position=position_dodge(0.5))+
     geom_errorbar(aes(ymin=fp-fpSD, ymax=fp+fpSD), width=1,
                 position=position_dodge(0.5)) +
     facet_grid(~ Predictor)+
     theme_minimal() +
     theme_bw()+
     xlab("") + ylab("False Positives") + #ylim(-.05,.5) +
     scale_color_discrete(name="Resampling Technique")+
     guides(shape=FALSE, linetype=FALSE)+
     theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

#TN
tnplot <- ggplot(pr_results_gm12878_summ, aes(x=Resolution, y=tn, color=Resampling, group=Resampling)) +
     geom_line(size=2, position=position_dodge(0.5))+
     geom_point(size=5, position=position_dodge(0.5))+
     geom_errorbar(aes(ymin=tn-tnSD, ymax=tn+tnSD), width=1,
                 position=position_dodge(0.5)) +
     facet_grid(~ Predictor)+
     theme_minimal() +
     theme_bw()+
     xlab("") + ylab("True Negatives") + #ylim(-.05,.5) +
     scale_color_discrete(name="Resampling Technique")+
     guides(shape=FALSE, linetype=FALSE)+
     theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

#FN
fnplot <- ggplot(pr_results_gm12878_summ, aes(x=Resolution, y=fn, color=Resampling, group=Resampling)) +
     geom_line(size=2, position=position_dodge(0.5))+
     geom_point(size=5, position=position_dodge(0.5))+
     geom_errorbar(aes(ymin=fn-fnSD, ymax=fn+fnSD), width=1,
                 position=position_dodge(0.5)) +
     facet_grid(~ Predictor)+
     theme_minimal() +
     theme_bw()+
     xlab("") + ylab("False Negatives") + #ylim(-.05,.5) +
     scale_color_discrete(name="Resampling Technique")+
     guides(shape=FALSE, linetype=FALSE)+
     theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))
```
